A Smart Robotic Cart Prototype using RF Signal Strength

### 2021-09-27 presIEEE-ROSE2021-BrBeAlShMi.tex
IEEE ROSE 2021 - presentation slides final version 1.0

@@

\subsection{Block Diagrams}
\begin{frame}{Block Diagrams}
  \begin{block}{}
    Two main components of system
    \begin{itemize}
      \item Mobile Cart
      \item Remote Target
    \end{itemize}
    System Block Diagram shown in Fig. \autoref{fig:sysBlockDiag}
  \end{block}
  \begin{figure}[b]
    \centering
    \includegraphics[width=\textwidth]{figs/systemBlockDiagram.pdf}
    \caption{Block Diagram of the Robotic Cart System}
    \label{fig:sysBlockDiag}
  \end{figure}
\end{frame}

@@

\begin{frame}{Block Diagrams}
  \begin{block}{}
    Remote Target Subsystem Block Diagram shown in Fig. \autoref{fig:sysRemoteBlockDiag}
  \end{block}
  \begin{figure}[b]
    \centering
    \includegraphics[width=\textwidth]{figs/remoteBlockDiagram.pdf}
    \caption{Block Diagram of Remote Target Subsystem}
    \label{fig:sysRemoteBlockDiag}
  \end{figure}
\end{frame}

@@

\begin{frame}{Block Diagrams}
  \begin{block}{}
    Mobile Cart Subsystem Block Diagram shown in Fig. \autoref{fig:sysMobileBlockDiag}
  \end{block}
  \begin{figure}[b]
    \centering
    \includegraphics[width=\textwidth]{figs/mobileCartBlockDiagram.pdf}
    \caption{Block Diagram of Mobile Cart Subsystem}
    \label{fig:sysMobileBlockDiag}
  \end{figure}
\end{frame}

>>>>

\usepackage{tikz}
% load libraries
\usetikzlibrary{backgrounds,calc,patterns,decorations.pathmorphing,decorations.markings,snakes}
\def\smgrid{0.5}

@@

\subsection{Block Diagrams}
\begin{frame}{Block Diagrams}
  \begin{block}{}
    Two main components of system
    \begin{itemize}
      \item Mobile Cart
      \item Remote Target
    \end{itemize}
    System Block Diagram shown in Fig. \autoref{fig:sysBlockDiag}
  \end{block}
  \begin{figure}[b]
    \centering
    % \includegraphics[width=0.2\textwidth]{figs/systemBlockDiagram.pdf}
    \begin{tikzpicture}    
      \tikzstyle{every node} = [font=\footnotesize];
      \tikzstyle{block} = [draw, rectangle, fill=blue!15, rounded corners, minimum height=0.5 cm, minimum width=0.5cm];
      \tikzstyle{pinstyle} = [pin edge={to-,thin,black}];
      \node[block,text width= 2.0cm, text centered](mobileCart){Mobile cart};
      \node[block,text width= 2.0cm, text centered, below of=mobileCart, node distance=1.25cm](remote){Remote};
      % Connections
      \draw[stealth-stealth,ultra thick]
      (mobileCart.south) --(remote.north);
      % Layers
      \begin{pgfonlayer}{background}
        \filldraw[fill=red!10,draw = red,dashed,ultra thick, rounded corners]                
        ($(remote.south west) + (-1.5*\smgrid,-0.25*\smgrid)$)node[](tmp1){} rectangle ($(mobileCart.north east) + (1.2*\smgrid,1.5*\smgrid)$)node[](tmp2){};
        \draw
        ($(mobileCart.north) + (-0.25*\smgrid,0.75*\smgrid)$)node{\textbf{Mobile cart system}};
        % %%% Inputs and outputs
        \draw[stealth-,thick]
        ($(tmp1)+(0,4.5*\smgrid)$) --node[near end,above]{Power}++(-3.0*\smgrid,0);
        \draw[stealth-,thick]
        ($(tmp1)+(0,3*\smgrid)$) --node[near end,above]{On/Off switch}++(-3.0*\smgrid,0);
        \draw[stealth-,thick]
        ($(tmp1)+(0,0.5*\smgrid)$) --node[near end,above]{Motion control}++(-3.0*\smgrid,0);
        \draw[-stealth,thick]
        ($(tmp2)+(0,-2.75*\smgrid)$) --node[very near end,above]{Cart position trajectory}++(4.0*\smgrid,0);
      \end{pgfonlayer}
    \end{tikzpicture}  
    \caption{Block Diagram of the Robotic Cart System}
    \label{fig:sysBlockDiag}
  \end{figure}
\end{frame}

@@

\begin{frame}{Block Diagrams}
  \begin{block}{}
    Remote Target Subsystem Block Diagram shown in Fig. \autoref{fig:sysRemoteBlockDiag}
  \end{block}
  \begin{figure}[b]
    \centering
    % \includegraphics[width=\textwidth]{figs/remoteBlockDiagram.pdf}
    \begin{tikzpicture}    
      \tikzstyle{every node} = [font=\tiny];
      \tikzstyle{block} = [draw, rectangle, fill=orange!15, rounded corners, minimum height=0.5 cm, minimum width=0.5cm];
      \tikzstyle{pinstyle} = [pin edge={to-,thin,black}];
      \node[block,text width= 2.5cm, text centered](rfTransceiverModule){RF transceiver module};
      % Connections
      % \draw[stealth-stealth,ultra thick]
      % (mobileCart.south) --(remote.north);
      % Layers
      \begin{pgfonlayer}{background}
        \filldraw[fill=green!10,draw = blue,dotted,thick, rounded corners]                
        ($(rfTransceiverModule.south west) + (-0.25*\smgrid,-0.25*\smgrid)$)node[](tmp1){} rectangle ($(rfTransceiverModule.north east) + (0.25*\smgrid,0.75*\smgrid)$)node[](tmp2){};
        \draw
        ($(rfTransceiverModule.north) + (-0.25*\smgrid,0.5*\smgrid)$)node{\textbf{Remote}};
        % %%% Inputs and outputs
        \draw[stealth-,thick]
        ($(tmp1)+(0,1.75*\smgrid)$) --node[near end,above]{Battery power}++(-3.0*\smgrid,0);
        \draw[stealth-,thick]
        ($(tmp1)+(0,0.5*\smgrid)$) --node[very near end,above]{Incoming RF messages}++(-3.5*\smgrid,0);
        \draw[-stealth,thick]
        ($(tmp2)+(0,-1.0*\smgrid)$) --node[midway,above]{Outgoing RF messages}++(5.25*\smgrid,0);
      \end{pgfonlayer}
    \end{tikzpicture}  
    \caption{Block Diagram of Remote Target Subsystem}
    \label{fig:sysRemoteBlockDiag}
  \end{figure}
\end{frame}

@@

\begin{frame}{Block Diagrams}
  \begin{block}{}
    Mobile Cart Subsystem Block Diagram shown in Fig. \autoref{fig:sysMobileBlockDiag}
  \end{block}
  \begin{figure}[b]
    \centering
    % \includegraphics[width=\textwidth]{figs/mobileCartBlockDiagram.pdf}
    \begin{tikzpicture}[scale=1.0,transform shape]    
      \tikzstyle{every node} = [font=\tiny];
      \tikzstyle{block} = [draw, rectangle, fill=orange!15, rounded corners, minimum height=0.6 cm, minimum width=0.5cm];
      \tikzstyle{pinstyle} = [pin edge={to-,thin,black}];
      \node[block,text width= 1.0cm, text centered](embeddedComputer){Embedded computer};
      \node[block,text width= 1.0cm, text centered, right of=embeddedComputer, node distance=2.5cm](DcMotors){DC motors};
      \node[block,text width= 1.5cm, text centered, below of=DcMotors, node distance=0.75cm](omnidirectionalRfTransciever){Omnidirectional RF transceiver};
      \node[block,text width= 1.5cm, text centered, below of=embeddedComputer, node distance=1.5cm](multiplexer){Multiplexer};
      \node[block,text width= 1.5cm, text centered, below of=multiplexer, node distance=1.0cm](RFReceiver1){Direction sensitive RF receiver};
      \node[block,text width= 1.5cm, text centered, below of=RFReceiver1, node distance=1.0cm](RFReceiver2){Direction sensitive RF receiver};
      \node[block,text width= 1.5cm, text centered, right of=RFReceiver1, node distance=2.5cm](RFReceiver3){Direction sensitive RF receiver};
      \node[block,text width= 1.5cm, text centered, right of=RFReceiver2, node distance=2.5cm](RFReceiver4){Direction sensitive RF receiver};
      % Connections
      \draw[stealth-,thick]
      (embeddedComputer.165) --node[near end,above]{Battery power}++(-2.5*\smgrid,0);
      \draw[stealth-,thick]
      (embeddedComputer.-165) --node[near end,below]{ON/OFF switch}++(-2.5*\smgrid,0);
      \draw[-stealth,thick]
      (embeddedComputer.0) --(DcMotors.180);
      \draw[-stealth,thick]
      (DcMotors.0) --node[midway,above]{Wheel velocities}++(2.5*\smgrid,0);
      \draw[-stealth,thick]
      (omnidirectionalRfTransciever.0) --node[near end,above]{Outgoing RF signals}++(2.75*\smgrid,0);
      \draw[stealth-,thick]
      (omnidirectionalRfTransciever.-170) --node[very near end,above]{Incoming RF signals}++(-7.5*\smgrid,0)node[](tmp1){};
      \draw[stealth-stealth,very thick]
      (multiplexer.90) --(embeddedComputer.-90);
      \draw[stealth-stealth,thick]
      (embeddedComputer.-45) |-(omnidirectionalRfTransciever.170);
      \draw[-stealth]
      ($(tmp1) + (\smgrid,0)$) |- (RFReceiver1.west);
      \draw[-stealth]
      ($(tmp1) + (\smgrid,0)$) |- (RFReceiver2.west);
      \draw[-stealth]
      ($(tmp1) + (\smgrid,0)$) |- ($(RFReceiver2.south)+(0,-0.5*\smgrid)$) -| ($(RFReceiver3.east)+(0.5*\smgrid,0)$) -- (RFReceiver3.east);
      \draw[stealth-]
      (RFReceiver4.east) -- ++(0.5*\smgrid,0);
      \draw[stealth-stealth]
      (RFReceiver1.east) -- ++(0.5*\smgrid,0)|-(multiplexer.-10);
      \draw[stealth-stealth]
      (multiplexer.10) -| (RFReceiver3.north);
      \draw[stealth-stealth]
      (RFReceiver2.east) -- ++(0.75*\smgrid,0)|-(multiplexer.-5);
      \draw[stealth-stealth]
      (RFReceiver4.west) -- ++(-0.5*\smgrid,0)|-(multiplexer.0);

      % Layers
      \begin{pgfonlayer}{background}
        \filldraw[fill=green!10,draw =blue,dotted,thick, rounded corners]                
        ($(RFReceiver2.south west) + (-0.25*\smgrid,-0.25*\smgrid)$) rectangle ($(DcMotors.north east) + (0.75*\smgrid,0.75*\smgrid)$);
        \draw
        ($(embeddedComputer.north) + (2*\smgrid,0.4*\smgrid)$)node{\textbf{Mobile cart}};
      \end{pgfonlayer}
    \end{tikzpicture}  
    \caption{Block Diagram of Mobile Cart Subsystem}
    \label{fig:sysMobileBlockDiag}
  \end{figure}
\end{frame}
